A Switching Planner for Combined Task and Observation Planning

### 2010-11-23 subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/conc.tex
New structure again.

>>>>

One theoretical criticism of switching continual planning concerns
interleaved sequential and decision-theoretic sessions failing to make
any progress towards the POMDP objectives. For example, in the worst
case we could have each sequential session producing an identical
plan, and each decision-theoretic session rejecting it without further
sensing. Although this has not been an issue in our work so far, it
must be dealt with rigorously moving forward. We propose a good way of
mitigation this problem is by using a {\em motivational} component
that maintains a {\em dynamic} reward model for sensing.
